### 2014-05-21 intro.tex
Add Remy graph to intro

Today's congestion-control protocols generally pay attention to a
small number of signals derived from packets arriving at the receiver,
or acknowledgments arriving back at the sender. Classical TCP schemes,
such as NewReno~\cite{newreno} and Cubic~\cite{cubic}, attempt to
detect packet loss as a proxy for in-network buffer
overflow. Delay-based schemes such as Vegas~\cite{vegas} detect
increasing round-trip delay, as a proxy for growing standing queues
inside the network.

Researchers and practitioners have proposed that the network should
provide additional information helpful for inferring the presence of
congestion~\cite{ecn,xcp,rcp}, but these schemes have not been widely
deployed.

Sprout and Remy have found that more useful information is available
from the data already provided by today's networks. In particular,
estimates of the rates of packet transmission and reception proved to
be crucial to helping these systems outperform existing algorithms.

\begin{figure}
\caption{Sprout measures the \textbf{rate} of packet arrivals at the
  receiver, forecasts the time required to drain the current queue,
  and tries to steer this quantity not to exceed a tenth of a
  second. Based on this technique, Sprout achieves less end-to-end
  delay than the other algorithms, while achieving almost as much
  throughput as TCP Cubic. From Figure~\ref{f:allgraphs} (Verizon LTE
  Downlink).}

@@

\def\svgwidth{\textwidth}\footnotesize\import{dotgraphs3/}{VerizonLTE-Downlink-minus1.pdf_tex}
\end{figure}

>>>>

Today's congestion-control protocols generally pay attention to a
small number of signals derived from packets arriving at the receiver,
or acknowledgments arriving back at the sender. Classical TCP schemes,
such as NewReno~\cite{newreno} and Cubic~\cite{cubic}, attempt to
detect packet loss as a proxy for in-network buffer
overflow. Delay-based schemes such as Vegas~\cite{vegas} detect
increasing round-trip delay as a proxy for growing standing queues
inside the network.

Researchers and practitioners have proposed that the Internet provide
additional information helpful for inferring the presence of
congestion~\cite{ecn,xcp,rcp,vcp}, but these schemes have not been
widely deployed. Sprout and Remy have found that more useful signals
can already be gleaned from today's networks. In particular, estimates
of the \emph{rates} of packet transmission and reception proved to be
crucial to helping these systems outperform existing algorithms.

%\begin{figure}
%\caption{
\noindent \begin{minipage}{\textwidth}

\textcolor{white}{.}\hspace{\parindent} Sprout measures the \textbf{rate} of packet arrivals at the receiver,
forecasts the time required to drain the current queue, and tries to
steer this quantity not to exceed a tenth of a second. Based on this
technique, Sprout achieves less end-to-end delay than the other
algorithms, while achieving close to the throughput of TCP
Cubic. From Figure~\ref{f:allgraphs} (Verizon LTE Downlink):
%}

@@

\def\svgwidth{\textwidth}\footnotesize\import{dotgraphs3/}{VerizonLTE-Downlink-minus1.pdf_tex}
\end{minipage}
%\end{figure}

\vspace{\baselineskip}
\enlargethispage{\baselineskip}

%\begin{figure}
%\caption{
\noindent \begin{minipage}{\textwidth}

\textcolor{white}{.}\hspace{\parindent} A Remy-generated algorithm, or
RemyCC, measures the \textbf{rate} of acknowledgment arrivals, and the
\textbf{rate} of transmission implied by the echoed sender timestamps
in those acknowledgments. We can quantify the value of these signals
by removing one of them and rerunning the optimization process. The
results are markedly worse with either signal removed.  From
Figure~\ref{f:tpdelaydb4}:
%}

\begin{center}
%\includegraphics[width=0.8 \columnwidth]{eth8-annotated.pdf}
\def\svgwidth{0.8 \textwidth}\footnotesize\input{eth8-annotatedb.pdf_tex}
\end{center}
\end{minipage}

%\end{figure}
